\chapter{Modeling Photovoltaics}\label{chapter:modeling_pvs}

In this chapter, \textbf{Modeling Photovoltaics}, we systematically review the
various types of abstractions in photovoltaics, starting from solar cells and
ending with solar arrays.

We start by observing how solar cell models can have differing granularities in
their composition and in how they address an array of internal qualities and
external environs that influence real world performance. Alongside defining
these models, we also propose modifications that may improve their accuracy and
precision, and consider tradeoffs that may occur in nonnominal conditions. After
defining these models, we then present an in-depth methodology for evaluating
them; we construct a dataset of solar cell \ac{I-V} curves characterized for use
on the \ac{LHRs} solar vehicle, then define techniques for extracting model
parameters for each cell. We proceed to use those model parameters to predict
their behavior in different conditions, and evaluate how they perform in terms
of model accuracy and precision.

We select the `best' set of solar cell models and use them as
building blocks to build larger models, namely those for solar modules. These
solar modules can take multiple shapes and sizes, and may exhibit reverse bias
behavior in the event of photovoltaic mismatch, a phenomenon caused by
nonuniform cells in series or in parallel. We also extend the module model by
adding a bypass diode in antiparallel, and discussing how solar cell reverse
bias behavior may drive their turn on conditions and mismatch mitigation
effects. From these solar module models, we formulate a metric to measure
mismatch, and propose suggestions and observations on how module size and cell
characteristics may influence the total efficiency of the module. Insights
developed in this section will later on become heuristics and algorithms for
optimizing module design in \autoref{chapter:optimizing_pvs}. We extend the test
methodology used for evaluating solar cells to solar modules, and validate
whether the module models pass muster.

% , either through manufacturing defects
% or lighting and thermal gradients across the module.

Finally, we take these solar module models and combine them together to form a
cohesive solar array model. From this model, we observe how the individual
module effects can generate a global \ac{I-V} curve with local and global
maxima, and discuss how this curve impacts the way the larger photovoltaic
system interacts with solar arrays. We also perform array testing using the
\ac{LHRs} solar array, and compare a simulated version of the array test with
real world data to determine a final, holistic evaluation of the models used.

\input{chapters/chapter_modeling_pvs/modeling_solar_cells/main.tex}
\input{chapters/chapter_modeling_pvs/modeling_solar_modules/main.tex}
\input{chapters/chapter_modeling_pvs/modeling_solar_arrays/main.tex}

\section{Conclusion}\label{sec:modeling_pvs_conclusion}

%TODO: conclusion for Chapter 1
\todo[inline]{Insert conclusion on chapter topics and results.}
