\chapter{Modeling Photovoltaics}\label{chapter:modeling_pvs}

In this chapter, \textbf{Modeling Photovoltaics}, we systematically review the
various types of abstractions in photovoltaics, starting from solar cells and
ending with solar arrays.

We start by observing how solar cell models themselves can have differing
granularities in their composition and how they address an array of internal
qualities and external environs that influence real world performance. We also
propose modifications that may improve their accuracy and precision, and
consider tradeoffs that may occur in nonnominal conditions. We then evaluate
these models against a dataset of solar cells characterized for use on the
\ac{LHRs} vehicle, and then use the `best' set of models to predict solar cell
behavior in larger contexts.

These larger contexts start with the formation of solar modules that can take
multiple shapes and sizes. We attempt to use the base set of models to
understand how different configurations of solar modules may be affected by
photovoltaic mismatch, a phenomenon caused by nonuniform cells in series or in
parallel, either through manufacturing defects or lighting and thermal
gradients across the module. We also add a bypass diode component in
antiparallel to the solar module models in order to evaluate their turn-on
conditions and mismatch mitigation effects. From these solar module models, we
formulate a metric to measure mismatch, and propose suggestions on module size
and bypass diode selection that can minimize mismatch. These suggestions will
become heuristics and algorithms for optimizing module design later on in
\autoref{chapter:optimizing_pvs}.

Finally, we take these solar module models and combine them together to form a
cohesive solar array model. From this model, we observe how the individual
module effects can generate a global \ac{I-V} curve with local and global
maxima, and discuss how this curve impacts how the larger photovoltaic system
interacts with solar arrays.

\newpage
\input{chapters/chapter_1/chapter_1_section_1.tex}
\newpage
\input{chapters/chapter_1/chapter_1_section_2.tex}
\newpage
\input{chapters/chapter_1/chapter_1_section_3.tex}
\newpage
\input{chapters/chapter_1/chapter_1_section_4.tex}
\newpage
\input{chapters/chapter_1/chapter_1_section_5.tex}
\newpage
\input{chapters/chapter_1/chapter_1_section_6.tex}
\newpage
\input{chapters/chapter_1/chapter_1_section_7.tex}
\newpage
\input{chapters/chapter_1/chapter_1_section_8.tex}

\dots
%TODO: conclusion for Chapter 1
\todo{Insert conclusion on chapter topics and results.}